The Exoplanet Orbit Database 2, 2014 updates

### 2014-03-13 draft/ms.tex

%------------------------------------------------------------------------------
% Figure: single planet page
\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../fig/wasp-14b.eps}
\caption{An example page for an individual exoplanet (WASP-14b in this
  case). The numbers listed in each field contain links to the
  reference on ADS. In this example for WASP-14b, we provide the plot
  for the phased RVs, but we are yet to implement such feature for all
  planets with available RV data.}
\label{fig:individual}
\end{figure}

@@

\end{enumerate}
\item Microlensing planets

\item Timing planets

@@

ZZZ (1) We have a list of criteria for 'robustly detected' imaging planets (on our methodology web page) - do we have similar lists of criteria regarding 'robust detections' for microlensing, timing, and astrometry planets?

No, not really.  As I think we discuss in the last EOD paper (check) we relax some conditions for transiting planets (we don't have to have a measured RV amplitude, for instance).  There have been no astrometric planets.  Timing planets must have dynamically stable orbits and, ideally, show multiple complete orbits (see Jackson Norris's paper for a discussion of difficulties with timing planets, also cite recent papers by Rob Wittenmyer).  In general, we accept microlensing planets that are appear in refereed journals as having unambiguously planetary masses.

@@

We have had two major updates since \cite{Wright2011}. We included Kepler planet candidates and other planets on exoplanets.org. Although they are not included in the EOD, we reported them on our website to help the users explore them and use them easily. We also have added some new fields, removed obsolete fields and revised them as necessary.

@@

SXW acknowledges support from PSARC.

>>>>

%------------------------------------------------------------------------------
% Figure: single planet page
\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../fig/wasp-14b.eps}
\caption{An example page for an individual exoplanet (WASP-14b in this
  case). The numbers listed in each field contain links to the
  reference on NASA ADS. In this example for WASP-14b, we provide the plot
  for the phased RVs, but we are yet to implement such feature for all
  planets with available RV data.}
\label{fig:individual}
\end{figure}

@@

\end{enumerate}
\item Microlensing planets:\\
We accept microlensing planets that appear in refereed journals as
having unambiguously planetary masses (planet host mass ratio,
$q<0.024$). In cases of ambiguity, we consult with QUACBED.

\item Timing planets:\\
 Timing planets must have dynamically stable orbits and, ideally, show
 multiple complete orbits (e.g., see \citealt{Wittenmyer2012},
 \citealt{Horner2012}, and \citealt{Wittenmyer2013}).

@@

ZZZ mention there have been no astrometry planets so far, but we do
plan to include them if any robust detections occur.

@@

We have had two major updates since \cite{Wright2011}. First, we
changed the scope of the EOD. We removed the limit on the type of the
host star. We included the planets discovered by various methods
(e.g. timing) in the EOD. We also have added some new fields, removed
obsolete fields and revised them as necessary.

Second, we included Kepler planet candidates and other planets on
exoplanets.org. Although they are not included in the EOD, we reported
them on our website to help the users explore them and use them
easily.

ZZZ add summary for Onsi's section.

@@

SXW acknowledges support from PSARC. This research has made use of
NASA's Astrophysics Data System Bibliographic Services (ADS).

### 2014-03-13 draft/references.tex

@@

>>>>

\bibitem[Horner et al.(2012)]{Horner2012} Horner, J., Wittenmyer, R.~A., 
Hinse, T.~C., \& Tinney, C.~G.\ 2012, \mnras, 425, 749 % dynamic
                                % analysis on timing planet

@@

\bibitem[Wittenmyer et al.(2012)]{Wittenmyer2012} Wittenmyer, R.~A., 
Horner, J., Marshall, J.~P., Butters, O.~W., 
\& Tinney, C.~G.\ 2012, \mnras, 419, 3258 % dynamic analysis on timing
                                % planets

\bibitem[Wittenmyer et al.(2013)]{Wittenmyer2013} Wittenmyer, R.~A., 
Horner, J., \& Marshall, J.~P.\ 2013, \mnras, 431, 2150 % dynamic
                                % analysis on timing planets
